\documentclass[a4paper]{scrbook}

\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{url}
\usepackage{relsize}
\usepackage{hyperref}
\usepackage{tgtermes}
\usepackage{ifthen}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{color}

\lstset{frame=tb,
  language=c++,
  aboveskip=5mm,
  belowskip=5mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{blue},
  keywordstyle=\color{red},
  commentstyle=\color{pink}\string,
  stringstyle=\color{green},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace these values
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\thesistitleDE}{Linux-Kernel-Treiber\\I2C Sensor und OLED Display}
\newcommand{\thesistitleEN}{Linux Kernel Driver\\I2C Sensor and OLED Display}
\newcommand{\student}{Nik Amir Syazwan Bin Abdul Aziz}
\newcommand{\matrnr}{00819429}
\newcommand{\stammnr}{00819429}
\newcommand{\submissiondate}{02.\ Juli 2023}
\newcommand{\supervisor}{Herr Tobias Gent}
\newcommand{\secsupervisor}{Herr Sergej Lamert}
\newcommand{\faculty}{Angewandte Informatik}

\newcommand{\studies}{Bachelor Angewandte Informatik}

\newcommand{\degree}{Bachelor of Engineering (B.Eng.)}

\renewcommand*{\UrlFont}{\ttfamily\smaller\relax}

\begin{document}
\pagestyle{headings}
\pagenumbering{roman}
\input{title}

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
As the usage of Linux becoming more popular in recent years, the development of linux drivers has improved significantly to
help and ease the users around the world. These drivers can be as simple as hardware driver for basic computer device
such as mouse, keyboard to much more complicated devices such as microprocessor and microcontroller for developers. The present 
report aims to outline the design, development, and implementation of a Linux kernel driver for I2C (Inter-Integrated Circuit) sensors 

The report begins by providing an overview of I2C communication and its significance in connecting various devices, especially 
sensors, to a Linux-based system. The characteristics and advantages of I2C bus architecture are discussed, emphasizing its 
suitability for sensor applications. The subsequent sections delve into the methodology employed for designing and implementing 
the Linux kernel driver for I2C sensors. The driver development process involves understanding the hardware specifications of the target sensor, 
defining necessary data structures and functions, and integrating them into the Linux kernel source code.

Additionally, the report discusses the challenges encountered during the driver development process, including data type problem, time management issues and 
lack of experience issue. The solutions and workarounds implemented to overcome these challenges are presented, 
highlighting the critical thinking and problem-solving skills employed.

In conclusion, the development and implementation of a Linux kernel driver for I2C sensors presented in this report provide a solid foundation 
for seamless integration and efficient utilization of I2C sensors within Linux-based systems.


\tableofcontents

\cleardoublepage%
\setcounter{page}{1}
\pagenumbering{arabic}
\input{main}
\input{methodology}
\input{hardware}
\input{software}
\input{usage}
\input{conclusion}

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}
